What We Eval in the Shadows

### 2021-04-15 paper/main.tex
Update the data.table example

\mypara{Variable lookup and values.}
This corresponds to minimized expressions \c{X}, \c{V}. We also include here lookup to slots in a list or data frame, \ie minimized expression \c{\$}.
It is the predominant usage of \eval in Base, through function \c{match.args}. In CRAN, it correlates with more exotic environments passed to \eval.

The dominant site in numbers of calls in CRAN, in the custom object system of \emph{ggplot2}, \c{ggproto}, also evaluates a variable \c{`\_inherit`} in the definition environment of the class. It leads to a large diversity of environments, many being package environment or package environments wrapped in \c{new}.

@@

A peculiar use of \eval is to bypass some checks performed to accept code submitted to CRAN. For example, bindings can be \emph{locked} in an environment, \ie forbidding its value to be modified. The binding can be unlocked though by calling \c{unlockBinding} but packages in CRAN are forbidden to use that function.  Package \emph{data.table} bypasses this restriction by building a call piece by piece, to unlock binding \c{.N}. The call is then evaluated.

\begin{lstlisting}
if (locked.N) eval(call("unlockBinding", ".N", parent.frame()))  
\end{lstlisting}

>>>>

\mypara{Variable lookup and values.}
This corresponds to minimized expressions \c{X}, \c{V}. We also include here lookup to slots in a list or data frame, \ie minimized expression \c{\$}.
It is the predominant usage of \eval in Base, through function \c{match.args}. In CRAN, it correlates with more exotic environments passed to \eval.
The dominant site in numbers of calls in CRAN, in the custom object system of \emph{ggplot2}, \c{ggproto}, also evaluates a variable \c{`\_inherit`} in the definition environment of the class. It leads to a large diversity of environments, many being package environment or package environments wrapped in \c{new}.

@@

A peculiar use of \eval is to bypass some checks performed to accept code submitted to CRAN. For example, bindings can be \emph{locked} in an environment, \ie forbidding its value to be modified. The binding can be unlocked though by calling \c{unlockBinding} but packages in CRAN are forbidden to use that function.  Package \emph{data.table} bypasses this restriction by building a call piece by piece, to unlock binding \c{.N}. The call is then evaluated. Now that \c{.N} is unlocked, it can be assigned to. Instead of using \eval to assign in the parent frame, they rather use the more specialized function \c{assign}.

\begin{lstlisting}
if (locked.N) eval(call("unlockBinding", ".N", parent.frame()))  
assign(".N", nrow(x), envir=parent.frame(), inherits=FALSE)
\end{lstlisting}
